Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-06 doc/main_jfm.tex
fixed up repulsion definition

The second part of the imposed forces and torques comes from repulsion
between proximal particles. We define 
\begin{align}
%  \label{eqn:REPUL}
%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
%  \\
%
  \label{eqn:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, \\
  \label{eqn:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    (\xx - \aa_i)^{\perp} \cdot 
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, 
\end{align}
\todo[inline]{Repulsion force is a function of only the distance between
the Janus particles instead of the integral around the particles.}
where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
pair of particles. The repulsion profile $P(r)$ is zero for distances
$r$ larger than a repulsion length scale $\rho_0$. As
such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque} ignore
particles $\Gamma_j$ outside a tubular neighborhood of $\Gamma_i$. For
$0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is
sufficiently large to prevent particle collisions. The total imposed
force and torque are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

>>>>

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed as $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
define the repulsion force and torque
\begin{align}
%  \label{eqn:REPUL}
%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
%  \\
%
  \label{eqn:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|) \\
  \label{eqn:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|) 
\end{align}
where $\aa_i$ is the center of particle $i$. The repulsion profile
$P(r)$ is zero for distances $r$ larger than a repulsion length scale
$\rho_0$. As such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque}
ignore particles $\Gamma_j$ outside a tubular neighborhood of
$\Gamma_i$. For $0 \leq r < \rho_0,$ we use $P(r) = M(1 -
\sin(r/\rho_0))$ where $M$ is sufficiently large to prevent particle
collisions. The total imposed force and torque are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}
